Paper TITLE

### 2016-08-05 code/Paper.Rmd
minor grammer

library(ggplot2)
library(dplyr)
library(readr)
library(stringr)
library(xml2)
library(rvest)
library(tidyr)
library(purrr)
library(maps)
library(ggthemes)
```

@@

  clean_years %>%
    mutate(per = cut(per, 
                     breaks = c(0, 1, 2, Inf),
                     labels = c("1", "2", "3 or more")))  %>%
    group_by(year, per) %>%  
    # Take the median instead of mean to avoid extreme observations skewing the 
    # result.
    summarise(new_y = median(burden, na.rm = T)) %>%
    ggplot(aes(x = year,   
                      y = new_y,   
                      colour = per)) +  
    geom_line() +
    labs(colour = "Household size",
         x = "Year",
         y = "Median burden") +
    theme_tufte()

@@

usa_map <- map_df %>% 
  ggplot() +  
  geom_polygon(aes(x=long, 
                   y = lat, 
                   fill = zinc2_median, 
                   group = group)) + 
  coord_fixed(1.3) +
  theme_minimal() +
  scale_x_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  scale_y_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  labs(fill = "Median income") +
  scale_fill_distiller(limits = c(25000, 42000), 
                                 breaks = sort(unique(map_df$zinc2_median),
                                               decreasing = T),
                                 palette = "Greens", 
                                 direction = 1,
                                 guide = "legend")
```

@@

ggplot(counts, aes(x = year, 
                   y = percent,
                   fill = fmtincrelpovcat)) + 
  geom_area(alpha = 0.8) +
  # Use a nice colour palette
  scale_fill_brewer(palette = "RdYlGn", 
                    # Reverse the order of legend items to match the
                    # stacking order
                    guide = guide_legend(reverse=TRUE)) +
  labs(title = "Amount of households relative to poverty line",
       x = "Year",
       y = "Precent of households",
       fill = "Household income
relative to poverty income") +
  theme_tufte()
```

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line() + 
  labs(title = "Relationship between Household \nIncome and Burden", 
       y = "Household Income ($)", x = "Year", color = "Burden") +
  theme_tufte()

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line() + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) +
  labs(title = "Relationship between Household \nIncome and Burden", 
       y = "Household Income ($)", x = "Year", color = "Burden") +
  theme_tufte()

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line() + 
  labs(title = "Relationship between Monthly \nHousing Costs and Burden", 
       y = "Monthly Housing Costs ($)", x = "Year", color = "Burden") +
  theme_tufte()

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line() + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) + 
  labs(title = "Relationship between Monthly \nHousing Costs and Burden", 
       y = "Monthly Housing Costs ($)", x = "Year", color = "Burden") +
  theme_tufte()

@@

clean_sample <- read_csv("../data/clean_years.csv")
clean_sample %>% filter(fmtstructuretype != ".") %>% 
      # Use NSE
      group_by_("year", "fmtstructuretype") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","increlamipct", ",na.rm=T)"))) %>%  
      # Use NSE
      ggplot(aes_string(x = "year",   
                        y = "new_y",   
                        colour = "fmtstructuretype")) +  
      geom_line() +
  labs(title="Income compared to area's median grouped by house type",
       colour = "Structure Type",
       y="Income percentage of area median income",
       x = "Year") +
  theme_tufte()

@@

```{r, fig.width=12, fig.height=6, echo = F, message=F,error=F, warning=FALSE}
assisted = clean_sample %>% filter(!is.na(assisted)) %>% 
      # Use NSE
      group_by_("assisted", "fmtcostmedrelamicat") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","burden", ",na.rm=T)"))) %>% 
      ungroup %>% 
      mutate(assisted = as.factor(assisted))
ggplot(assisted, aes(y = new_y,   
                  x = fmtcostmedrelamicat,
                  fill = assisted, group = assisted)) +  
  geom_bar(
           stat="identity") + 
  labs(title="Burden based on Median housing cost with assistance",
       y="Burden",
       x = "",
       fill="Assistance") + 
  scale_y_continuous(limits=c(0,1)) +
  scale_fill_brewer("Assistance", 
                    labels = c("Without Assistance", 
                               "With Assistance"),
                    palette = "Set2")  +
  coord_flip() +
  theme_tufte()
```

@@

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(aplmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() +
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "Median Income Adjusted \nfor the Number of People by Region") + 
  scale_color_discrete(name = "Region", labels = regionNames) +
  theme_tufte()

@@

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(ablmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() +
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "Median Income Adjusted \nfor Number of Bedrooms by region") + 
  scale_color_discrete(name = "Region", labels = regionNames) +
  theme_tufte()

>>>>

library(ggplot2)
library(dplyr)
library(readr)
library(stringr)
library(xml2)
library(rvest)
library(tidyr)
library(purrr)
library(maps)
```

@@

  clean_years %>%
    mutate(per = cut(per, 
                     breaks = c(0, 1, 2, Inf),
                     labels = c("1", "2", "3 or more")))  %>%
    group_by(year, per) %>%  
    # Take the median instead of mean to avoid extreme observations skewing the 
    # result.
    summarise(new_y = median(burden, na.rm = T)) %>%
    ggplot(aes(x = year,   
                      y = new_y,   
                      colour = per)) +  
    geom_line() +
    labs(colour = "Household size",
         x = "Year",
         y = "Median burden")

@@

usa_map <- map_df %>% 
  ggplot() +  
  geom_polygon(aes(x=long, 
                   y = lat, 
                   fill = zinc2_median, 
                   group = group)) + 
  coord_fixed(1.3) +
  theme_minimal() +
  scale_x_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  scale_y_continuous(name = NULL,
                     labels = NULL,
                     breaks = NULL) +
  labs(fill = "Median income") +
  scale_fill_distiller(palette = "Blues",
                       direction = 1)

@@

ggplot(counts, aes(x = year, 
                   y = percent,
                   fill = fmtincrelpovcat)) + 
  geom_area(alpha = 0.5) +
  # Use a nice colour palette
  scale_fill_brewer(palette = "RdBu", 
                    # Reverse the order of legend items to match the
                    # stacking order
                    guide = guide_legend(reverse=TRUE)) +
  labs(title = "Amount of households relative to poverty line",
       x = "Year",
       y = "Precent of households",
       fill = "Household income
relative to poverty income") 
```

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line() + 
  labs(title = "Relationship between Household \nIncome and Burden", 
       y = "Household Income ($)", x = "Year", color = "Burden")

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line() + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) +
  labs(title = "Relationship between Household \nIncome and Burden", 
       y = "Household Income ($)", x = "Year", color = "Burden")

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line() + 
  labs(title = "Relationship between Monthly \nHousing Costs and Burden", 
       y = "Monthly Housing Costs ($)", x = "Year", color = "Burden")

@@

  ggplot(aes_string(x = "year", y = "new_y", color = "fmtburden")) + 
  geom_line() + 
  facet_wrap(~region, labeller = as_labeller(regionNames)) + 
  labs(title = "Relationship between Monthly \nHousing Costs and Burden", 
       y = "Monthly Housing Costs ($)", x = "Year", color = "Burden")

@@

clean_sample <- read_csv("../data/clean_years.csv")
clean_sample %>% filter(fmtstructuretype != ".") %>% 
      # Use NSE
      group_by_("year", "fmtstructuretype") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","increlamipct", ",na.rm=T)"))) %>%  
      # Use NSE
      ggplot(aes_string(x = "year",   
                        y = "new_y",   
                        colour = "fmtstructuretype")) +  
      geom_line() +
  labs(title="Income compared to area's median grouped by house type",
       colour = "Structure Type",
       y="Income percentage of area median income",
       x = "Year")

@@

```{r, fig.width=12, fig.height=6, echo = F, message=F,error=F, warning=FALSE}
assisted = clean_sample %>% filter(!is.na(assisted)) %>% 
      # Use NSE
      group_by_("assisted", "fmtcostmedrelamicat") %>%  
      # Take the median instead of mean to avoid extreme observations skewing the 
      # result.
      summarise_(new_y= as.formula(paste0("~ median(","burden", ",na.rm=T)"))) %>% 
      ungroup %>% 
      mutate(assisted = as.factor(assisted))
ggplot(assisted, aes(y = new_y,   
                  x = fmtcostmedrelamicat,
                  fill = assisted, group = assisted)) +  
  geom_bar(
           stat="identity") + 
  labs(title="Burden based on Median housing cost with assistance",
       y="Burden",
       x = "",
       fill="Assistance") + 
  scale_y_continuous(limits=c(0,1)) +
  scale_fill_manual("Assistance",labels=c("Without Assistance", "With Assistance"), values=c("black", "white")) +
  coord_flip()
```

@@

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(aplmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() +
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "Median Income Adjusted \nfor the Number of People by Region") + 
  scale_color_discrete(name = "Region", labels = regionNames)

@@

clean_years %>%
  group_by(year, region) %>%  
  # Take the median instead of mean to avoid extreme observations skewing the 
  # result.
  summarise(new_y = median(ablmed, na.rm = T)) %>%
  ggplot(aes(x = year,   
                  y = new_y,   
                  colour = region)) + geom_line() +
  labs(x = "Year", y = "Median Adjusted Income (per persons)", 
       title = "Median Income Adjusted \nfor Number of Bedrooms by region") + 
  scale_color_discrete(name = "Region", labels = regionNames)
